FoRTE baseline

### 2019-07-04 analysis/paper/paper.Rmd
Add Shannon diversity to all analyses

Across all variables, parameter uncertainty (across ensembles within each model configuration) was at least as large, and usually larger, than structural uncertainty (Figure 4).
The relative importance of parameter uncertainty varied with both model configuration and the variable in question. 
Allowing SLA and V~cmax~ to vary with light level (warm colors, as opposed to static traits -- cool colors) led to reduced predictive uncertainty for all four variables considered, with the largest uncertainty reduction for gross and net primary productivity.
Meanwhile, facilitating horizontal competition by enabling the finite canopy radius (dark colors; compared to closed canopy -- light colors) substantially reduced uncertainty in aboveground biomass and slightly reduced uncertainty in gross and net primary productivity.
Finally, using a multiple-scatter (secondary colors) rather than a two-stream (primary colors) radiative transfer scheme increased uncertainty in leaf area index and aboveground biomass, but did not have a consistent effect on uncertainty in predictions of productivity.

>>>>

Across all variables, parameter uncertainty (across ensembles within each model configuration) was at least as large, and usually larger, than structural uncertainty (Figure 4).
The relative importance of parameter uncertainty varied with both model configuration and the variable in question. 
Allowing SLA and V~cmax~ to vary with light level (warm colors, as opposed to static traits -- cool colors) led to reduced predictive uncertainty for all four variables considered, with the largest uncertainty reduction for gross and net primary productivity.
Meanwhile, facilitating horizontal competition by enabling the finite canopy radius (dark colors; compared to closed canopy -- light colors) substantially reduced uncertainty in aboveground biomass and diversity, and slightly reduced uncertainty in gross and net primary productivity.
Finally, using a multiple-scatter (secondary colors) rather than a two-stream (primary colors) radiative transfer scheme increased uncertainty in leaf area index, aboveground biomass, and diversity, but did not have a consistent effect on uncertainty in predictions of productivity.
